CKY Parsing With Independence Constraints

### 2015-07-03 paper.tex
Add explanation

\subsection{Results}
\label{sec-4-4}

\label{sec:linear-classifier}
For use as input to the parser, we select the $p,P_{1},P_{3}$
feature configuration, and show more detailed results in
Table \ref{tbl:classifier-results-linear}. We used a threshold on the
score output by the classifier to reverse some of the classifier's
decisions in a post-process step. Although it doesn't improve on the
classifier in accuracy, the \texttt{precision} threshold did slightly improve in
F$_{\text{0.5}}$, a measure which favors precision over recall.

@@

We used the modified Stanford Parser described above, with an unlexicalized
grammar\footnote{The grammar was extracted using the Stanford Parser with command-line options \texttt{-acl03pcfg -noRebinarization -compactGrammar 1}} extracted from the WSJ sections 02-21, and evaluated its performance
on section 22 using output from the classifier as constraints. For the baseline,
the parser was given null constraints.

>>>>

\subsection{Results}
\label{sec-4-4}
\label{sec:linear-classifier}

To avoid degrading the accuracy of the parser as much as possible, we selected
the feature configuration based on F$_{\text{0.5}}$ score, a measure which
favors precision over recall. We chose $p,P_{1},P_{3}$ over $p,P_{0},P_{1}$
because the former had a slight edge in precision and fewer features.

More
detailed results are shown in Table \ref{tbl:classifier-results-linear}. We used
a threshold on the score output by the classifier to reverse some of the
classifier's decisions in a post-process step. Although it doesn't improve on
the classifier in accuracy, the \texttt{precision} threshold did slightly
improve in F$_{\text{0.5}}$.

@@

We used the modified Stanford Parser described above, with an unlexicalized
grammar\footnote{The grammar was extracted using the Stanford Parser with command-line options \texttt{-acl03pcfg -noRebinarization -compactGrammar 1}} extracted from the WSJ sections 02-21, and evaluated its performance
on section 22 using output from the classifier as constraints. For the baseline,
the parser was given null constraints. The accuracies and times shown are those reported
by the Stanford Parser.
